An Imaging Search for Circumstellar Companions of Sirius B

### 2021-09-20 paper/paper.tex
reorganize paper for easier submission

\documentclass[twocolumn]{aastex631}
\usepackage{cleveref}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{makecell}

@@

We used three metrics to determine the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve. The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics. The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above. We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}. The collapsed residual frames along with the above metrics for each algorithm for each epoch are in \cref{sec:adi-results}.

A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). For PCA, NMF, and GreeDS algorithms, we increased the number of components from 1 to 10, creating a residual cube for each iteration. We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}). In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in \cref{sec:adi-results}.

@@

The reduced images do not show consistent or significant evidence for a substellar companion. The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\qty{0.3}{\au} (\ang{;;0.13}; 1.6 FWHM) from the center. The February epoch also shows a blob at a similar separation in the reduced image which does not appear in the STIM map. The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions. Nonetheless, we estimated astrometry for blobs from each epoch (\cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}. We generated $10^4$ orbits, none of which contained the points from each epoch (\cref{sec:orbits}). We take this as direct evidence against the blobs being substellar companions of any kind.

@@

\input{sections/adi_results}

>>>>

\documentclass[twocolumn,linenumbers]{aastex631}
\usepackage{cleveref}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{makecell}

@@

We used three metrics to determine the performance of each algorithm, the signal-to-noise ratio (S/N) significance map, the standardized trajectory intensity mean map \citep[STIM map;][]{pairet_stim_2019}, and the contrast curve. The significance and STIM maps assign a likelihood to each pixel for the presence of a companion using different assumptions of the residual statistics. The contrast curve determines the sensitivity of a 5$\sigma$ statistical detection through repeated injection and retrieval of planetary signal as processed by one of the ADI algorithms above. We calculate both the Gaussian contrast and the Student-t corrected contrast, which accounts for the small-sample statistics in each annulus \citep{mawet_fundamental_2014}. The collapsed residual frames along with the above metrics for each algorithm for each epoch are in section~\ref{sec:adi-results}.

A common problem when using subspace-driven post-processing algorithms like PCA, NMF, or GreeDS is choosing the size of the subspace (i.e., the number of components). For PCA, NMF, and GreeDS algorithms, we increased the number of components from 1 to 10, creating a residual cube for each iteration. We chose 10 for the maximum number of components because we saw a dramatic decline in contrast sensitivity after the first few components (\cref{fig:pca-contrast-curves}). In our analysis we employed the STIM largest intensity mask map \citep[SLIM map;][]{pairet_signal_2020} as an ensemble statistic. The SLIM map calculates the average STIM map from many residual cubes along with the average mask of the $N$ most intense pixels in each STIM map. A real companion ought to be present in many different residual cubes from the same dataset, so this ensemble approach can give us a probability map without predetermining the number of components. The collapsed residual frames, average STIM map, SLIM map, and contrast curves for each epoch for each of the above algorithms are in section~\ref{sec:adi-results}.

@@

The reduced images do not show consistent or significant evidence for a substellar companion. The STIM probability maps for the 2020-11-21 and 2020-11-28 epochs suggest evidence for some blobs $\sim$\qty{0.3}{\au} (\ang{;;0.13}; 1.6 FWHM) from the center. The February epoch also shows a blob at a similar separation in the reduced image which does not appear in the STIM map. The lack of statistical evidence in the February epoch and the significance maps as well as the proximity to the central star both reduce the probability of these blobs being true companions. Nonetheless, we estimated astrometry for blobs from each epoch (\cref{tbl:astrometry}) and tried fitting Keplerian orbits using the ``Orbits for the Impatient'' algorithm \citep[OFTI;][]{blunt_orbits_2017}. We generated $10^4$ orbits, none of which contained the points from each epoch (section~\ref{sec:orbits}). We take this as direct evidence against the blobs being substellar companions of any kind.

@@

\input{adi_results_full}
